Additional analysis for articulation transition points

### 2020-07-29 script/RNotebook/additional020420/articulation.Rmd
update analysis with the new trimmed
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Additional analysis for transition points"
output: html_notebook
---
Description: These are some additional analyses for transition points.

## Articulation
How does it look like articulation transition points?
Posthoc prediciton: Participants would have a larger separation betwenn the end of legato and the beginning of staccato.

@@

# read csv
df_kot <- fread("./../trimmed/data_kot.csv")

# only transition points for arituclation
df_kot_trans <- df_kot[Skill == "articulation" & Subcomponent != "Legato" & Subcomponent != "Staccato"]
```

```{r stats1, echo = TRUE}
# For each individual
art_trans <- df_kot_trans[, .(N = length(KOT), Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Condition, Subcomponent)]
print(art_trans)
# Group
art_trans_all <- art_trans[, .(N = length(Mean), Mean = mean(Mean), SEM = sd(Mean)/sqrt(length(Mean))), by = .(Condition, Subcomponent)]
print(art_trans_all)
# Stats
# normality check
art_trans_norm <- by(art_trans$Mean, list(art_trans$Condition, art_trans$Subcomponent), shapiro.test)
print(art_trans_norm)
# ezAnova
art_trans_aov <- ezANOVA(
  data = df_kot_trans
  , dv = .(KOT)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
print(art_trans_aov)
```

>>>>

---
title: "Additional analysis for articulation transition points"
output: html_notebook
---
Description: These are some additional analyses for articulation transition points.

## Articulation
How does it look like articulation transition points?

Post-hoc prediction: Participants would have **a larger separation** between the end of legato and the beginning of staccato.

@@

# read csv
dt_kot <- fread("./../trimmed/data_kot.csv")

# only transition points for arituclation
dt_kot_trans <- dt_kot[Skill == "articulation" & Subcomponent != "Legato" & Subcomponent != "Staccato"]
```

```{r stats1, echo = TRUE}
# For each individual
art_trans <- dt_kot_trans[, .(N = length(KOT), Mean = mean(KOT), SD = sd(KOT)), by = .(SubNr, Condition, Subcomponent)]
print(art_trans)
# Group
art_trans_all <- art_trans[, .(N = length(Mean), Mean = mean(Mean), SEM = sd(Mean)/sqrt(length(Mean))), by = .(Condition, Subcomponent)]
print(art_trans_all)
# Stats
# normality check
art_trans_norm <- by(art_trans$Mean, list(art_trans$Condition, art_trans$Subcomponent), shapiro.test)
print(art_trans_norm)

# Converting variables to Factor
dt_kot_trans$SubNr <- factor(dt_kot_trans$SubNr)
dt_kot_trans$Condition <- factor(dt_kot_trans$Condition)
dt_kot_trans$Subcomponent <- factor(dt_kot_trans$Subcomponent)

# ezAnova
art_trans_aov <- ezANOVA(
  data = dt_kot_trans
  , dv = .(KOT)
  , wid = .(SubNr)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
print(art_trans_aov)
```
